\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rahul Marban}
% \address{Chennai}
\address{\href{mailto:rahulmarban@gmail.com}{rahulmarban@gmail.com} \\ \href{tel:+918248668008}{8248668008} \\ \href{https://linkedin.com/in/rahul-marban}{linkedin.com/in/rahul-marban} \\ \href{https://github.com/Rahuletto}{github.com/Rahuletto} \\ \href{https://marban.is-a.dev}{marban.is-a.dev}}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

% \begin{rSection}{SUMMARY}

% <SUMMARY>

% \end{rSection}


%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
    \textbf{Software Engineer Intern} \hfill Dec 2025 - May 2026\\
AskMeIdentity \hfill \textit{Bengaluru}

- Designed and implemented the UI and UX for the LMX platform, delivering 10+ production screens and defining user flows from wireframes to deployed features.
- Led the redesign of 4+ core modules across the application suite, standardizing layout patterns and improving visual consistency across products.
- Built a cross platform desktop application using Electron, implementing 3 major feature flows including authentication, content access, and update handling.

\textbf{Research Intern} \hfill Mar 2025 - Feb 2026\\
Samsung R\&D Institute India - Bangalore \hfill \textit{Chennai}

- Working as a Technical researcher with team of 4 for Developing AI solutions, focusing on innovative approaches and optimizing solutions
- Collaborating on industry-level as Research Intern in the Samsung PRISM program

\textbf{Software Engineer Intern} \hfill Oct 2025 - Dec 2025\\
EmendoAI \hfill \textit{San Francisco Bay Area}

- Collaborated with design and backend teams to deliver updates faster and maintain production quality during UI and logic changes.
- Authored comprehensive technical documentation for testing workflows and architecture components, improving onboarding speed for new contributors by 30\%.
- Fixed 50+ bugs, including navigation regressions and data overflow issues, directly improving platform stability and preventing user-facing crashes.

\textbf{Frontend Developer Intern} \hfill Jan 2025 - Jul 2025\\
SRM Innovation and Incubation Centre \hfill \textit{Chennai, Tamil Nadu, India}

- Rebuilt 60+ pages from scratch to create a faster, more modern, user-friendly and responsive website with smooth animations for 3+ sites.
- Achieved 25\% increase in user engagement and a 10\% reduction in bounce rate through optimizations in performance, accessibility, and SEO.
- Coordinated and maintained version control workflows, ensuring smooth collaboration and code integration across updates.

\end{rSection}

% \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
    \textbf{\href{https://github.com/Rahuletto/lavalamp}{lavalamp}} \(\mid\) \textbf{Agentic AI, Typescript, Workers AI, Flue}
\begin{itemize}
\itemsep -3pt{}
\item An open-source Cloudflare-native coding agent harness enabling AI-assisted software development directly from the terminal.
\item Designed core infrastructure including semantic code indexing, a hash-anchored file editing engine improving edit reliability by 42\%, resumable agent sessions, and approval-based command execution.
\item Architected an extensible multi-agent framework with expert subagents and Cloudflare Workers AI integration, providing secure, local-first AI development workflows.
\end{itemize}

\textbf{\href{https://github.com/Rahuletto/agent-orchestrator}{agent-orchestrator}} \(\mid\) \textbf{Typescript, Node.js, Redis}
\begin{itemize}
\itemsep -3pt{}
\item Built a recursive orchestration engine supporting multi-stage task pipelines with dynamic agent spawning.
\item Designed execution system enabling N-level task delegation across dependent workflows
\item Implemented asynchronous execution handling multiple concurrent task flows (20+ agents) with state propagation and state persistence using Redis
\item Generates a dependency graph with the agents and follows a master-delegator model in a form of layers in recursive way to complete the goal
\end{itemize}

\textbf{\href{https://github.com/Rahuletto/bullet}{bullet}} \(\mid\) \textbf{Typescript, Nuclei, BBOT, SQLi}
\begin{itemize}
\itemsep -3pt{}
\item Built an agentic AI security platform that reasons over 7+ web application surfaces, generates attack hypotheses, prioritizes high-signal leads, and autonomously executes multi-step tool-calling workflows.
\item Engineered a 25+ phase reconnaissance and vulnerability-validation pipeline covering authentication, SQL injection, XSS, SSRF, business logic, API discovery, and JavaScript analysis.
\item Integrated knowledge-graph reasoning to correlate endpoints, exposed secrets, authentication context, findings, and attack chains into structured security reports.
\end{itemize}
\end{rSection}
% \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

% \begin{rSection}{LANGUAGES}

% \begin{itemize}
%     English (PROFESSIONAL WORKING), Hindi (ELEMENTARY), Tamil (NATIVE OR BILINGUAL)
% \end{itemize}

% \end{rSection}



%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

% \begin{rSection}{CERTIFICATIONS}

%     \begin{itemize}
%         MongoDB Associate Developer, Red Hat Enterprise Linux Automation with Ansible (RH294 - RHA) - Ver. 9.0, Samsung PRISM, Red Hat Certified Specialist in Containers, Exploratory Data Analysis for Machine Learning,  Machine Learning Onramp, Deep Learning Onramp, AWS Educate Introduction to Generative AI, Database Structures and Management with MySQL, Devshouse'25, Digital Image Processing, Image Processing Onramp, The Great Bengaluru Hackathon, Innofusion'25, Ultron 8.0, Vertex Innovate Organizer,  Oracle Cloud Infrastructure 2024 Certified Foundations Associate, Advanced Programming in Swift, Hack Day - First Edition, Supervised Machine Learning: Regression and Classification 
%     \end{itemize}

%     \end{rSection}


%     \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

% \vspace{1.5em}

\begin{rSection}{Education}
    \href{https://www.linkedin.com/school/s.r.m.-institute-of-science-&-technology-chennai/}{SRM Institute of Science and Technology} \hfill Expected 2027\\
\textbf{BTech} Computer Science Engineering with AIML \hfill \textit{CGPA: 9.41}
\end{rSection}

% \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

    \begin{tabular}{@{}>{\bfseries}l @{\hspace{4ex}}p{0.75\textwidth} @{}}
    Languages & Python, Typescript, Javascript, Go\\
    Frameworks & Pytorch, YOLO, LangGraph, AI SDK, FastAPI, Next.js, ReactJS, Express, Hono, Fiber\\
    Others & OpenAI, HuggingFace, Supabase, PostgreSQL, Git
    % Soft Skills & Attention to Detail, Problem-Solving, Team Collaboration, Leadership\\
    \end{tabular}

    \end{rSection}

%     \vspace{1.5em}



\end{document}
