\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rahul Marban}
% \address{Chennai} 
\address{\href{mailto:rahulmarban@gmail.com}{rahulmarban@gmail.com} \\ \href{tel:+918248668008}{+91 8248668008} \\ \href{https://linkedin.com/in/rahul-marban}{linkedin.com/in/rahul-marban} \\ \href{https://github.com/Rahuletto}{github/Rahuletto} \\ \href{https://marban.is-a.dev}{marban.is-a.dev}}

\begin{document}

%----------------------------------------------------------------------------------------
%	SUMMARY
%----------------------------------------------------------------------------------------

% \begin{rSection}{SUMMARY}

% <SUMMARY>

% \end{rSection}


%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\begin{rSection}{EXPERIENCE}
    \textbf{Frontend Developer Intern} \hfill Jan 2025 - Present\\
SIIC Chennai \hfill \textit{Chennai, Tamil Nadu, India}


\begin{itemize}
\itemsep -3pt{}
\item Revamped over 60 web pages to modernize the website, elevating user engagement and ensuring an intuitive interface that resulted in a measurable increase in user satisfaction metrics gathered through post-launch surveys.
\item Collaborated with a small team of 2 developers over 6 months to deliver a high-quality web solution.
\item Maintained consistent communication to gather requirements, provide updates, and successfully developed 3+ websites.
\end{itemize}
\textbf{Chief Design Officer} \hfill Nov 2024 - Present\\
Turn2Law \hfill \textit{Chennai, Tamil Nadu, India}


\begin{itemize}
\itemsep -3pt{}
\item Led the creative direction for a team of 5+ designers and developers, ensuring alignment with brand vision and user needs.
\item Transformed the platforms UI/UX by designing intuitive navigation features, leading to a 20\% surge in user engagement and enhanced customer satisfaction metrics based on direct feedback from usability testing sessions.
\end{itemize}
\textbf{Full Stack Software Development Intern} \hfill Aug 2024 - Present\\
Neugence Technology Pvt Ltd \hfill \textit{Remote}


\begin{itemize}
\itemsep -3pt{}
\item Evolved and launched 2 fully functional websites as a frontend developer, ensuring seamless user experiences and adherence to project deadlines.
\item Tailored and implemented responsive web designs, increasing user engagement by 38\% through refined accessibility and cross-device compatibility.
\item Migrated the entire codebase to Vite, reducing development cycle times by 25\%, resulting in faster feature delivery and team productivity better than before.
\end{itemize}

\end{rSection}

% \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	PROJECTS
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}    
    \textbf{\href{https://github.com/Rahuletto/simply-djs}{simply-djs}} | \textbf{(Typescript, DiscordJS, NPM, MongoDB, NodeJS)}
\begin{itemize}
\itemsep -3pt{}
\item Developed SimplyDJS, a third-party utility library for Discord.JS, streamlining complex bot functionalities with minimal code, leading to 400K+ annual downloads and widespread adoption across the developer community.
\item Providing a developer-friendly and feature rich module, allowing Discord bot developers to integrate more than 30 features without having to write complex logic
\item Maintained for more than 2 years with regular performance optimizations, security enhancements, and continuous feature updates compatible with the latest Discord.JS version.
\item Reached more than 75 stars, 30+ forks, and 350+ commits on GitHub, with more than 5 active contributors to the project.
\end{itemize}
\textbf{\href{https://github.com/Rahuletto/ClassPro}{ClassPro}} | \textbf{(Typescript, React, Go, NextJS, Supabase)}
\begin{itemize}
\itemsep -3pt{}
\item Serving over 15,000+ monthly active users with 1.1M+ page views per month, ensuring scalability and stability for the students.
\item Incorporated a Golang fiber server to scrape data which resulted in 40\% faster data scraping and fetches reducing the wait time
\item Optimized platform performance to handle peak traffic, ensuring 99.9\% uptime and seamless access during critical academic periods.
\end{itemize}
\textbf{\href{https://github.com/Rahuletto/gitMyStat}{gitMyStat}} | \textbf{(Typescript, React, NextJS, Satori)}
\begin{itemize}
\itemsep -3pt{}
\item Accelerated SVG generation by 20\% using Satori in NextJS, achieving render times under 500 milliseconds and outpacing competitors.
\item Built a builder website enabling users to assemble and fine-tune GitHub profile designs and statistics, boosting user engagement by 20\%.
\item Optimized backend architecture to handle 500+ concurrent requests, ensuring zero downtime during peak usage
\end{itemize}
\end{rSection}
% \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	LANGUAGES
%----------------------------------------------------------------------------------------

% \begin{rSection}{LANGUAGES}

% \begin{itemize}
%     English (Professional), Hindi (Elementary), Tamil (Native)
% \end{itemize}

% \end{rSection}




%----------------------------------------------------------------------------------------
%	CERTIFICATIONS
%----------------------------------------------------------------------------------------

% \begin{rSection}{CERTIFICATIONS}

%     \begin{itemize}
%          Oracle Cloud Infrastructure 2024 Certified Foundations Associate, Advanced Programming in Swift, Hack Day - First Edition, Supervised Machine Learning: Regression and Classification , Viksit Bharat Quiz Challenge, Programming in Java, Smart India Hackathon 2024, Dark Patterns Buster Hackathon 2023, Design and Develop, Preface - UI/UX Design, Responsive Web Design, C Programming - Professional Level, C Programming, Certificate of Participation in PixelX-24 hours Designathon, Go (Basic) Certificate, Node (Basic) Certificate, Problem Solving (Basic) Certificate, Python (Basic) Certificate, Python for Machine Learning, React (Basic) Certificate
%     \end{itemize}

%     \end{rSection}


%     \vspace{1.5em}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

% \vspace{1.5em}

\begin{rSection}{Education}
    \textbf{B.Tech} Computer Science Engineering with AIML \hfill Expected 2027\\
\href{https://www.linkedin.com/school/s.r.m.-institute-of-science-&-technology-chennai/}{SRM Institute of Science and Technology} \hfill \textit{CGPA: 9.36}

\end{rSection}

% \vspace{1.5em}


%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

    \begin{tabular}{@{}>{\bfseries}l @{\hspace{4ex}}p{0.75\textwidth} @{}}
    Languages & Javascript, Typescript, Python, C, Java, Go\\
    Frameworks & Next.js, ReactJS, Astro, Solid, Fresh, FastAPI, Pytorch, Express, Hono, Elysia, Fiber, React Native, Tauri, Framer Motion, TailwindCSS\\
    Soft Skills & Attention to Detail, Problem-Solving, Team Collaboration, Leadership\\
    \end{tabular}
    
    \end{rSection}
    
%     \vspace{1.5em}

    
    
\end{document}
